### 2020-12-31 ch/2-related-work.tex
Meager changes
I'm writing too slowly

\citet{arjovsky2019invariant} tackle a similar problem, but take a very different approach,
which they term ``Invariant Risk Minimization'', in contrast to the default method Empirical Risk Minimization.
They formalize the problem as one of different environments $e\in E$.

\citet{creager2020environment} compares itself directly to \citet{arjovsky2019invariant}.

--- --- --- --- --- ---

Similarly to \citet{wick2019unlocking},
\citet{blum2020recovering} consider label bias and sampling bias with evaluation on an unbiased ground truth test set.

>>>>

\citet{arjovsky2019invariant} tackle a similar problem, but take a very different approach,
which they term ``Invariant Risk Minimization'', in contrast to the default method Empirical Risk Minimization.
Just like the approach by \citet{kim2019learning}, 
As with \citet{kim2019learning},
the goal is to ignore spurious correlations that only appear in the very imperfect training set,
but not in the test set;
and they also perform experiments on Colored MNIST (see above).
They formalize the problem as one of different environments $e\in E$,
where each environment is a different, biased view of the same underlying data distribution.
The idea is to train a predictor that is simultaneously optimal for all the environments,
with the expectation that this generalizes to the test set.
This idea is formulated as a (untractable) bi-level, constrained optimization problem,
which they approximate with a tractable regularized optimization.

\citet{creager2020environment} build directly on \citet{arjovsky2019invariant}.
They aim to address the limitation that the environments -- that one wants to be invariant to -- have to be pre-defined.
Their contribution is to infer these environments instead,
based on identifying which environment splits would most negatively affect an ERM classifier.
Their experiments show that this can even approve upon hand-crafted environments;
experiments are performed on a synthetic dataset and Colored MNIST.
In contrast to \citet{kim2019learning} and \citet{arjovsky2019invariant},
the authors explicitly point out the connection to traditional fairness methods.

Finally, as mentioned in the beginning,
\citet{blum2020recovering} provide a formalization of a setting with label bias and sampling bias
and an unbiased ground truth test set.
This is similar to \citet{wick2019unlocking}.
